Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-09 paper/v2/paper-edited.tex
added to evaluation section

% Formal product construction
Let $a_i$ and $b_i$ denote states in the regular policy automata.
The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
%
The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $. That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
%
Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$. We use the notation $x \leq_{rank} y$ as a shorthand for $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.

@@

\begin{algorithm}[t!]
\caption{Failure Protection}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Protect($G$, $N_1$, $N_2$)}{}
  \If {$loc(N_1) \neq loc(N_2)$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \For {$x$ in adj($G$, $n_2$)}
      \If {\big($\exists y \in$ adj($G$,$n_1$), shadows $x$\big) \textbf{or} \\  
            \hspace{5.2em} \big($\exists y \in$ $G$, dominates $n_1$, shadows $x$\big)}
        \If {$(x,y)$ not marked $\wedge$ $x \leq_{rank} y$}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward. The idea is to encode the state of the automaton using BGP community values. Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR. For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else). If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.

@@

The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization. Our implementation performs partial minimization during generation by recognizing common cases where there is no restriction on exporting to or importing from neighbors.

@@

We apply \sysname on real policies for backbone and data center networks. Our mains goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.

@@

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the \sysname policies were 43 lines for the backbone network and 31 lines for the data center networks.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix since the compiler operates on each prefix in parallel. At their largest sizes, the per-prefix compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

@@

>>>>

% Formal product construction
Let $a_i$ and $b_i$ denote states in the regular policy automata.
The PGIR is constructed by adding an edge from $v_1 = (x, a_1, \dots, a_m)$ to $v_2 = (y, b_1, \dots, b_m)$ whenever $\sigma_i(a_i, y) = b_i$ for each $i$ and $(x,y) \in E$ is a valid topology link.
%
Additionally, we add edges from the start node $s$ to any $v = (x, a_1, \dots, a_m)$ when $\sigma_i(q_{0_i}, x) = a_i$ for each $i$.
%
The preference function $P$ for node $v = (x, a_1, \dots, a_m)$ is defined as $P(v) = \set{i~\vert~a_i \in F_i} $. That is, it records which preferences are achieved from each policy automaton for every node in the product construction.
%
Finally, there is an edge from each node in the PGIR such that $P(v) \neq \emptyset$ to the special end node $e$. We say that $x \leq_{rank} y$ if either $P(x) = P(y) = \emptyset$ or $min ~ P(x) \leq min ~ P(y)$, which simply states that paths that end at PGIR node $x$ are better than (lower rank) than paths that end at $y$.

@@

\begin{algorithm}[t!]
\caption{Failure Protection}
\label{alg:failures}
\begin{algorithmic}[1]
\Procedure{Protect($G$, $N_1$, $N_2$)}{}
  \If {$loc(N_1) \neq loc(N_2)$} \Return false
  \EndIf
  \State $q \gets Queue()$
  \State $q.Enqueue (N_1, N_2)$
  \While {$!q.Empty()$}
    \State $(n_1,n_2) \gets q.Dequeue()$
    \If {$n_1 \nleq_{rank} n_2$} 
      \Return false
    \EndIf
    \For {$x$ in adj($G$, $n_2$)}
      \If {\big($\exists y \in$ adj($G$,$n_1$), shadows $x$\big) \textbf{or} \\  
            \hspace{5.2em} \big($\exists y \in$ $G$, dominates $n_1$, shadows $x$\big)}
        \If {$(x,y)$ not marked}
          \State {mark $(x,y)$ as seen}
          \State $q.Enqueue(x,y)$
        \EndIf
      \Else { \Return $false$}
      \EndIf
    \EndFor
  \EndWhile
  \Return true
  \EndProcedure
\end{algorithmic}
\end{algorithm}

@@

Once we have the ordering on node preferences in the PGIR from the failure safety analysis, the translation to ABGP is straightforward. The idea is to encode the state of the automata using BGP community values. Each router will match based on its peer and a community value corresponding to the state of the PGIR, and then update the state before exporting to the neighbors permitted by the PGIR. For example, router $A$ in Figure~\ref{fig:example-compilation} will allow an announcement from $C$ with a community value for state $(3,2)$ (and deny anything else). If it sees such an announcement, it will remove the old community value, and add a new one for state $(4,2)$ before exporting it to $W$.

@@

The naive code generation algorithm described in Section~\ref{sec:compilation} is extremely memory inefficient since it generates a separate match-export pair for every unique in edge/out edge pair for every node in the product graph before minimization. Our implementation performs partial minimization during generation by recognizing common cases like when there is no restriction on exporting to or importing from neighbors.

@@

We apply \sysname on real policies for backbone and data center networks. Our main goals are to evaluate if its front-end is expressive enough for real-world policies and the time the compiler takes to generate router configurations.

@@

Not counting the lines for various definitions like prefix and customer groups or for prefix ownership constraints, which we cannot reveal because of confidentiality concerns, the routing policies for \sysname were 43 lines for the backbone network and 31 lines for the data center networks.

@@

All experiments are run on an 8 core, 3.6 GHz Intel Xeon processor running Windows 7.
%
Figure~\ref{fig:compilation-times} shows the compilation times for data centers (a), and backbone networks (b) of different sizes. For both policies, we measure the mean compilation time per prefix predicate since the compiler operates on each prefix predicate in parallel. Note that a single predicate can describe many prefixes, for example by matching on a disjunction of prefixes. At their largest sizes, the per-predicate compilation time is roughly 10 seconds for the data center network and 45 seconds for the backbone network.

@@

In both examples, we observe that our safety analysis algorithm for finding preferences is highly efficient, taking only a small fraction of the total running time. PGIR minimization is proportionally the most expensive compilation phase, however minimization can be capped after a certain number of iterations for larger networks if necessary. Both the backbone and data center networks policies we considered can be successfully compiled without minimization.
